---
title: "VA Monthly Rotation Report"
output: html_document
params:
  report_month: ""
  report_year: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = TRUE, warning = FALSE)
```

```{r run-report}
# Pass through Rmd params (set in Posit Connect job settings) as env vars
# so the underlying script can pick them up. Empty params -> use defaults
# (current month).
if (nzchar(params$report_month)) Sys.setenv(REPORT_MONTH = params$report_month)
if (nzchar(params$report_year))  Sys.setenv(REPORT_YEAR  = params$report_year)

# Write the .xlsx alongside the rendered .html so Connect can attach it
# to the scheduled-report email.
Sys.setenv(OUTPUT_DIR = ".")

source("va_monthly_report.R", echo = FALSE)
```

**Output file:** ``r fname``

| Metric | Value |
|---|---|
| Report month | `r month_label` |
| Residents in report | `r nrow(summary_wide)` |
| Total VA days logged | `r sprintf("%.1f", sum(summary_wide$Total_VA_Days, na.rm = TRUE))` |
| Raw VA rows pulled | `r nrow(va_data)` |
| Day-components after 1.0/date cap | `r nrow(va_capped)` |

The Excel workbook (`r basename(fname)`) is attached to this rendering; it
contains the full Summary, Daily Detail, Class Summary, and Assignment
Inventory tabs.
